NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-11-20 Manuscript/manuscriptPS.tex

    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18} &0    & 0   & 60:12 & ?     & 0   & 298  & ?  & ?  & \cite{??} \todoi{Data to be delivered by Melcr}  \\
    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18} &0\todoi{Concentration to be checked after the amount of ions and water is known.}    & 0.03 & 60:12 & ?     & ?   & 298  & ?  & ?  & \cite{??} \todoi{Data to be delivered by Melcr}  \\
    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18} &0\todoi{Concentration to be checked after the amount of ions and water is known.}    & 0.17 & 60:12 & ?     & ?   & 298  & ?  & ?  & \cite{??} \todoi{Data to be delivered by Melcr}  \\
    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18} &0\todoi{Concentration to be checked after the amount of ions and water is known.}    & 0.36 & 60:12 & ?     & ?   & 298  & ?  & ?  & \cite{??} \todoi{Data to be delivered by Melcr}  \\

>>>>

    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18} &0    & 0      & 60:12 & 3600  & 0   & 298  & 1000  & 1000  & \cite{lipid17_cacl_series}   \\
    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18} &0    & 0.08   & 60:12 & 3561  & 5   & 298  & 1000  & 1000  & \cite{lipid17_cacl_series}   \\
    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18} &0    & 0.13   & 60:12 & 3561  & 8   & 298  & 1000  & 1000  & \cite{lipid17_cacl_series}   \\
    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18} &0    & 0.20   & 60:12 & 3561  & 13  & 298  & 1000  & 1000  & \cite{lipid17_cacl_series}   \\
    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18} &0    & 0.41   & 60:12 & 3522  & 26  & 298  & 1000  & 1000  & \cite{lipid17_cacl_series}   \\
    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18} &0    & 0.62   & 60:12 & 3483  & 39  & 298  & 1000  & 1000  & \cite{lipid17_cacl_series}   \\
